KidsAIR: exposure model

### 2020-04-27 exposure_models.Rmd
exposure model updates

####### Format full data to use for analysis
analysis_data <- exposure_analysis_data_short %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  filter(area == "WMT") %>% 
  group_by(area, home) %>% 
  distinct(home, winter_id, .keep_all = TRUE) %>% 
  ungroup() %>% 
  mutate(moisture_closest_2level = cut(moisture_closest, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE),
         moisture_winter_2level = cut(mean_moisture_winter, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE)) %>% 
  mutate(temp_max_2level = cut(temp_indoor_max, breaks = c(0, 30, 100),
                                 labels = c("<30", "30+"),
                                 right = FALSE),
         temp_min_2level = cut(temp_indoor_min, breaks = c(0, 16.5, 100),
                                 labels = c("<16.5", "16.5+"),
                                 right = FALSE),
         rh_max_2level = cut(rh_indoor_max, breaks = c(0, 40, 100),
                                 labels = c("<40", "40+"),
                                 right = FALSE),
         rh_min_2level = cut(rh_indoor_min, breaks = c(0, 20, 100),
                                 labels = c("<20", "20+"),
                                 right = FALSE)) %>% 
  mutate(sums_mean_sampling_period_5 = sums_mean_sampling_period/5,
         temp_perc_25_2level = cut(temp_perc_25, breaks = c(0, 50, 100),
                                 labels = c("<50", "50+"),
                                 right = FALSE),
         temp_perc_27_2level = cut(temp_perc_27, breaks = c(0, 35, 100),
                                 labels = c("<35", "35+"),
                                 right = FALSE),
         temp_perc_30_2level = cut(temp_perc_30, breaks = c(0, 10, 100),
                                 labels = c("<10", "10+"),
                                 right = FALSE)) %>% 
  group_by(home) %>% 
  mutate(residents_smoke = if_else(winter_id == 1 & is.na(residents_smoke),
                                   lead(residents_smoke), residents_smoke)) %>% 
  ungroup() %>% 
  left_join(sums_temp_change, by = c("area", "home", "home_winter_id")) %>% 
  left_join(ambient_data, by = c("area", "home")) %>% 
  select(-starts_with("home_act")) %>% 
  left_join(home_activity_data, by = c("area", "home", "home_winter_id")) %>% 
  select(pm_mean_sampling_period, area, income_3level, 
                 stove_age_3level, home_windows_2level,
                 chimney_clean_3level, wood_collect_2level, 
                 home_act_door, home_act_smoking, home_act_sweep, home_act_windows, 
                 stove_grade_3level, moisture_closest_2level,
                 total_residents_2level, mean_temp_sampling_period_5) %>% 
  filter(!is.na(pm_mean_sampling_period))

@@

>>>>

####### Format full data to use for analysis
analysis_data <- exposure_analysis_data_short %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  #filter(area == "WMT") %>% 
  group_by(area, home) %>% 
  distinct(home, winter_id, .keep_all = TRUE) %>% 
  ungroup() %>% 
  mutate(moisture_closest_2level = cut(moisture_closest, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE),
         moisture_winter_2level = cut(mean_moisture_winter, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE)) %>% 
  mutate(temp_max_2level = cut(temp_indoor_max, breaks = c(0, 30, 100),
                                 labels = c("<30", "30+"),
                                 right = FALSE),
         temp_min_2level = cut(temp_indoor_min, breaks = c(0, 16.5, 100),
                                 labels = c("<16.5", "16.5+"),
                                 right = FALSE),
         rh_max_2level = cut(rh_indoor_max, breaks = c(0, 40, 100),
                                 labels = c("<40", "40+"),
                                 right = FALSE),
         rh_min_2level = cut(rh_indoor_min, breaks = c(0, 20, 100),
                                 labels = c("<20", "20+"),
                                 right = FALSE)) %>% 
  mutate(sums_mean_sampling_period_5 = sums_mean_sampling_period/5,
         temp_perc_25_2level = cut(temp_perc_25, breaks = c(0, 50, 100),
                                 labels = c("<50", "50+"),
                                 right = FALSE),
         temp_perc_27_2level = cut(temp_perc_27, breaks = c(0, 35, 100),
                                 labels = c("<35", "35+"),
                                 right = FALSE),
         temp_perc_30_2level = cut(temp_perc_30, breaks = c(0, 10, 100),
                                 labels = c("<10", "10+"),
                                 right = FALSE)) %>% 
  group_by(home) %>% 
  mutate(residents_smoke = if_else(winter_id == 1 & is.na(residents_smoke),
                                   lead(residents_smoke), residents_smoke)) %>% 
  ungroup() %>% 
  left_join(sums_temp_change, by = c("area", "home", "home_winter_id")) %>% 
  left_join(ambient_data, by = c("area", "home")) %>% 
  select(-starts_with("home_act")) %>% 
  left_join(home_activity_data, by = c("area", "home", "home_winter_id")) %>% 
  select(pm_mean_sampling_period, income_3level, 
         stove_age_3level, home_windows_2level,
         chimney_clean_3level, wood_collect_2level,
         stove_grade_3level)
  filter(!is.na(pm_mean_sampling_period)) 
  replace_with_na(replace = list(mean_temp_sampling_period_5 = "NaN"))

# Check % missing data
#mean(is.na(analysis_data))

@@

Looking at model selection and averaging after multiple imputation

```{r}
library(MAMI)
#library(Amelia)
library(mice)

# Using mice package

# Look for patterns in missing data
md.pattern(analysis_data)

# Impute missing data; m = 5 datasets (check % missing data and match)
imputed_data <- mice(analysis_data, m=5)
summary(imputed_data)

# Sample one of the imputed datasets
check1 <- complete(imputed_data, 3)

# Using MAMI package, perform model averaging and selection
model_ave <- mami(imputed_data, missing.data = "imputed", model = "gaussian",
                  outcome = "pm_mean_sampling_period",
                  method = "MA.criterion", criterion = "AIC",
                  inference = "+boot", B = 15, X.org = analysis_data, print.time = TRUE)

summary(model_ave)
plot(model_ave)
```
